
```{r}
install.packages("doMC", repos="http://R-Forge.R-project.org")
```

loading data :


```{r}
mtcars_df = data.frame(mtcars)
head(mtcars_df)
```


split data to train set and test set :


```{r}
library(caret)
mtcars_df_split = createDataPartition(mtcars_df$mpg, p = 0.80, list=FALSE)
mtcars_train_set = mtcars_df[mtcars_df_split,]
mtcars_test_set = mtcars_df[-mtcars_df_split,]
```


fitting model : 


```{r}
linear_model_mtcars = lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear + carb, data = mtcars_train_set)

summary(linear_model_mtcars)
```

Based on the t-stat, wt seems relevant. Furthermore other features like qsec, hp, disp also have big t-stat value.

-> wt = -4.74715
-> qsec = 2.14918
-> hp = -0.01274
-> disp = 0.02338


```{r}
coef(linear_model_mtcars)
```


performing ridge regression : 


```{r}
library(glmnet)
```


```{r}
library(doMC)
y = mtcars_train_set$mpg
x = data.matrix(mtcars_train_set[,c('cyl','disp','hp','drat','wt','qsec','vs','am','gear','carb')])
glm = glmnet(x,y, alpha= 0)
summary(glm)
```


```{r}
plot(glm)
```


```{r}
registerDoMC(core=2)
grid_lambda  = 10^seq(10,-2,length=100)
mtcars_cross_val_glm = cv.glmnet(x,y, alpha= 0, lambda = grid_lambda, parallel = TRUE, grouped=FALSE)
summary(mtcars_cross_val_glm)
```


```{r}
best_lambda_val = mtcars_cross_val_glm$lambda.min
best_lambda_val
```


```{r}
plot(mtcars_cross_val_glm) 
```


```{r}
mtcars_new_model = glmnet(x, y, alpha=0, lambda=best_lambda_val)
summary(mtcars_new_model)
```


```{r}
y_test = mtcars_test_set$mpg
x_test = data.matrix(mtcars_test_set[,c('cyl','disp','hp','drat','wt','qsec','vs','am','gear','carb')])
y_mtcars_predictions = predict(mtcars_new_model, s=best_lambda_val, newx=x_test)
```


results Sample Test :


```{r}
SST_mtcars = sum((y_test -mean(y_test))^2)
cat("SST : ",SST_mtcars)
SSE_mtcars = sum((y_mtcars_predictions -mean(y_test))^2)
cat("\nSSE : ", SSE_mtcars)
mtcars_R_sq = 1 - (SSE_mtcars/SST_mtcars)
cat("\nR -square : ",mtcars_R_sq)
```


Difference in coeffcient values of models can be seen below :


```{r}
coef(mtcars_new_model)
```


```{r}
coef(linear_model_mtcars)
```


It can be seen from new coefficent values that Ridge Regression did not do variable section (coff = 0). It performed 'Shrinkage'.


```{r}
plot(glm, xvar="lambda", label=TRUE)
```
